---
title: "Changing presentation-layout via spans"
format: 
  revealjs: 
    subtitle: "Default format: Figures to the left, bullets to the right"
---

# A presentation

## Default slide

**The default**

:::: {.columns}

::: {.column width="50%"}

```{r}
#| label: fig-exampleA
plot(cars)
```

```{r}
#| label: fig-exampleB
x <- seq(-pi, pi, 0.1)
plot(x, sin(x))
```

::: 

::: {.column width="50%"}

- text describing @fig-exampleA
    - look at all this data. Wow.
- or maybe also @fig-exampleB
    - note that the speaker-notes, accessible in speaker-view (press `s` on the webiste) are empty

::: 

:::: 

## Slide 2

- a normal side

## Intended goal

**The intended goal**

:::: {.columns}

::: {.column width="50%"}

```{r}
#| label: fig-exampleA2
plot(cars)
```

::: 

::: {.column width="50%"}
```{r}
#| label: fig-exampleB2
x <- seq(-pi, pi, 0.1)
plot(x, sin(x))
```

::: 

:::: 

::: {.notes}

- text describing @fig-exampleA2
    - look at all this data. Wow.
- or maybe also @fig-exampleB2
    - note that the speaker-notes, accessible in speaker-view (press `s` on the webiste) are empty

::: 

## Slide 4

- another normal side
