---
title: "Changing presentation-layout via spans"
format: 
  revealjs: 
    subtitle: "Default format: Figures to the left, bullets to the right"
params:
  hide_notes: FALSE
---

# A presentation

## Default slide

**The default**

:::: {.columns}

::: {.column width="50%"}

```{r}
#| label: fig-exampleA
plot(cars)
```

```{r}
#| label: fig-exampleB
x <- seq(-pi, pi, 0.1)
plot(x, sin(x))
```

::: 

::: {.column width="50%"}

- text describing @fig-exampleA
    - look at all this data. Wow.
- or maybe also @fig-exampleB
    - note that the speaker-notes, accessible in speaker-view (press `s` on the webiste) are empty

::: 

:::: 

## Slide 2

- a normal side

## Intended goal

**The intended goal**

:::: {.columns}

::: {.column width="50%"}

```{r}
#| label: fig-exampleA2
plot(cars)
```

::: 

::: {.column width="50%"}
```{r}
#| label: fig-exampleB2
x <- seq(-pi, pi, 0.1)
plot(x, sin(x))
```

::: 

:::: 

::: {.notes}

- text describing @fig-exampleA2
    - look at all this data. Wow.
- or maybe also @fig-exampleB2
    - note that the speaker-notes, accessible in speaker-view (press `s` on the webiste) are empty

::: 

## Slide 4

The intention is to use the dynamically change the output format between the one displayed on slide 3:



```{bash}
#| echo: true
#| eval: false
# Yield Format of slide 3:
quarto render about.qmd
```

and the one on slide 5 by executing:

```{bash}
#| echo: true
#| eval: false
# Yield Format of slide 5:
quarto render about.qmd --execute-params layout2.yml
```

to be applied on selective slides of a larger presentation.
To do so, I am attempting to wrap the various parts of the slide into parameter-conditionals as outlined in the [docs](https://quarto.org/docs/authoring/conditional.html#matching-against-metadata)

Unfortunately, this does not seem to work - or I might not understand how to correctly nest spans.
